Cloud Supercomputing

### 2019-04-11 writing/paper/paper.tex
Include MB's comments.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
In this paper we use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows\todo{LK: Heißt das so?}.
To include viscosity, we use the numerical flux of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous} to include the parabolic terms of the compressible Navier-Stokes equations.
This flux has already been applied to the \aderdg{} method in~\cite{dumbser2010arbitrary}.
\todo{Einordnung, Kontext zu giraldo, etc$\ldots$}

@@

We make the following contributions:
\begin{itemize}%
\item We extend the \exahypeengine{} to allow diffusive terms following the aforementioned numerical scheme.
\item We use this to provide an implementation of the compressible Navier-Stokes equations.
\item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows.
\end{itemize}

>>>>

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
In this paper we use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows\todo{LK: Heißt das so?}.
To include viscosity\todo{MB meint (zu recht), dass die viscosity unmotiviert ist.
  Lieber noch so 10--15 Zeilen drüber schreiben.}, we use the numerical flux of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous} to include the parabolic terms of the compressible Navier-Stokes equations.
This flux has already been applied to the \aderdg{} method in~\cite{dumbser2010arbitrary}.
\todo{Einordnung, Kontext zu giraldo, etc$\ldots$}

@@

We make the following contributions\todo{Feedback von MB: Besser hervorheben, warum diese Sachen interessant/neu sind.
Dumbser macht in seinen NS-DG papern keine komplexen Source terme, keine hydrostatic flows, etc.
}:
\begin{itemize}%
\item We extend the \exahypeengine{} to allow diffusive terms following the aforementioned numerical scheme.
\item We use this to provide an implementation of the compressible Navier-Stokes equations.
\item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows.
\end{itemize}
